Streaming CityJSON datasets

### 2024-05-01 paper/main.tex
Some sentence fixed

In Section~\ref{sec:experiments}, we describe  the open-source software we have developed to convert between CityJSON and CityJSONSeq files.
We also analyse the size of CityJSONSeq files versus CityJSON files, and that for several real-world datasets.
It can be observed that one advantage of CityJSONSeq, besides that files containing thousands of features can be processed with a low memory footprint, is that it compresses further the CityJSON files by around 12\%, sometimes more.
We discuss in Section~\ref{sec:experiments} the reasons for this interesting finding.

>>>>

In Section~\ref{sec:experiments}, we describe  the open-source software we have developed to convert between CityJSON and CityJSONSeq files.
We also analyse the filesizes of CityJSON and CityJSONSeq for several real-world datasets and synthetic datasets we built.
It can be observed that one advantage of CityJSONSeq, besides that files containing several thousands of features can be streamed, is that it compresses further the CityJSON files by around 12\%, sometimes more.
We discuss in Section~\ref{sec:experiments} the reasons for this interesting finding.
